Characterizing Stellar Streams by ML

### 2023-07-28 src/tex/ms.tex
[showyourwork] overleaf sync

            The astrometric track is modeled with a neural network in each phase space dimension, parameterized as a function of $\phi_1$. The neural network output for a single stream component is the mean location of the stream track in each dimension, $\mbs{\mu}_w(\phi_1 | q_i)$, and its associated covariance matrix $\mbs{\Sigma}_w(\phi_1 | q_i)$. The probability for the data is then
            \begin{equation}
                \pdf^{(S)}(\nth{\mbs{w}} | \mbs{\theta}, \phi_{1,i}, q_i) = \mcal{N}\left(\nth{\mbs{w}} | \mbs{\mu}_w\left(\phi_{1,i} | q_i \right), \mbs{\Sigma}_w\left(\phi_{1,i} | q_i \right) \right),
            \end{equation}
            where $\mbs{\theta}$ is the set of neural network parameters that define $\mbs{\mu}_w$ and $\mbs{\Sigma}_w$.
            In the simplest case, we take $\mbs{\Sigma}_w$ to be diagonal, consisting of both intrinsic dispersion for each dimension of $\mbs{w}$ and the data uncertainties added in quadrature.

@@

@@

        \begin{enumerate}
            \item A network per model component, e.g. one for the weights, one for the stream track and width, one for the background distribution.
        \end{enumerate}

>>>>

            The astrometric track is modeled with a neural network, encompassing each phase space dimension, parameterized as a function of $\phi_1$. The neural network output for a single stream component is the mean location of the stream track in each dimension, $\mbs{\mu}_w(\phi_1 | q_i)$, and its associated covariance matrix $\mbs{\Sigma}_w(\phi_1 | q_i)$. The probability for the data is then
            \begin{equation}
                \pdf^{(S)}(\nth{\mbs{w}} | \mbs{\theta}, \phi_{1,i}, q_i) = \mcal{N}\big(\nth{\mbs{w}} | \mbs{\mu}_w\left(\phi_{1,i} | q_i \right), \mbs{\Sigma}_w\left(\phi_{1,i} | q_i \right) \big),
            \end{equation}
            where $\mbs{\theta}$ is the set of neural network parameters that define $\mbs{\mu}_w$ and $\mbs{\Sigma}_w$.
            In the simplest case, we take $\mbs{\Sigma}_w$ to be diagonal, consisting of both intrinsic dispersion for each dimension of $\mbs{w}$ and the data uncertainties added in quadrature.

@@

            \todo[inline]{TODO:}
            \begin{enumerate}
                \item Not including isochrone parameters, e.g. age and metallicity
                \item integrating over $\gamma$ the model assumes a PDMF, e.g. Kroupa
            \end{enumerate}

            By integrating over $\gamma$ the model is not sensitive to

@@

        \begin{enumerate}
            \item A network per model component, e.g. one for the weights, one for the stream track and width, one for the background distribution.
            \item MLP for the components - lin / tanh + dropout
            \item Normalizing flow - specific pieces
        \end{enumerate}

        \begin{table}
            \centering
            \caption{MLP structure}
            \begin{tabular}{@{}ccc@{}}
            \toprule
            Layer & Shape & Param \# \\
            \midrule
            Linear & (1, 3) & 1  \\
            Tanh & (2, 3) & 1  \\
            Dropout & (2, 3) & 0  \\
            \bottomrule
            \end{tabular}
        \end{table}
